### 2020-01-31 cv_models.tex
more edits

We have examined the performance of the four quality (Frobenius norm, Spectral norm, Weighted Alpha, and $\alpha$-Norm) applied to each of the VGG, ResNet, ResNet-1K, and DenseNet series.
To start, Figure~\ref{fig:vgg-metrics} plots the four quality metrics versus the reported Test accuracies~\cite{pyTorchVgg}, as well as a basic linear regression line, 
%with the Root Mean Squared Error (RMSE) shown, 
for the pretrained models VGG11, VGG13, VGG16, and VGG19, with and without BatchNormalization.
\michael{These are all log norms, right?}
\michael{XXX.  WHERE IS RMSE.  IN THAT TABLE?}
All four metrics correlate quite well with the reported Top1 Accuracies, with smaller norms and smaller values of $\hat{\alpha}$ implying better generalziation (i.e., greater accuracy, lower error). 
Similar results (not shown) are obtained for the Top5 Accuracies.  
Notice that the log $\alpha$-Norm metric $\log\Vert\mathbf{W}\Vert)_{\infty}^{\infty}$ 
\michael{XXX IS THAT A TYPO} 
performs best, with an RMSE of $0.34$; and the second best metric is $\hat\alpha$, which is an approximate log $\alpha$-Norm metric.
\michael{Are those numbers stale, I don't see them, and some things seem in the other order.}
\michael{We should probably point to the table if we cite quantitative results.}

@@

Table \ref{table:cv-models} summarizes results for all four metrics (Frobenius norm, Spectral norm, Weighted Alpha, and $\alpha$-Norm) applied to the VGG, ResNet, ResNet-1K, and DenseNet series.
\michael{XXX.  AGAIN, WHERE IS RMSE, IN THAT TABLE?}

@@

For the ResNet-1K models, $\alpha$ also increases in the last few layers, but as the models get deeper, there is a wide range over which $\alpha$ values tend to remain small.
\michael{Can we say something about exceptions which are larger than for VGG or DenseNet.}
This is seen for other models in the ResNet-1K series, but it is most pronounced for the larger ResNet-1K (152) model, where $\alpha$ remains relatively stable at $\alpha\sim 2.0$, from the earliest layers all the way until we reach close to the final layers.

>>>>

We have examined the performance of the four quality (Frobenius norm, Spectral norm, Weighted Alpha, and $\alpha$-Norm) applied to each of the VGG, ResNet, ResNet-1K, and DenseNet series.
To start, Figure~\ref{fig:vgg-metrics} plots the four quality metrics versus the reported Test accuracies~\cite{pyTorchVgg}, as well as a basic linear regression line, 
%with the Root Mean Squared Error (RMSE) shown, 
for the pretrained models VGG11, VGG13, VGG16, and VGG19, with and without BatchNormalization.
\michael{These are all log norms, right?}
\michael{XXX.  WHERE IS RMSE.  IN THAT TABLE?}
All four metrics correlate quite well with the reported Top1 Accuracies, with smaller norms and smaller values of $\hat{\alpha}$ implying better generalziation (i.e., greater accuracy, lower error). 
Similar results (not shown) are obtained for the Top5 Accuracies.  
Notice that the log $\alpha$-Norm metric $\log\Vert\mathbf{W}\Vert)_{\infty}^{\infty}$ 
\michael{XXX IS THAT A TYPO} 
performs best, with an RMSE of $0.34$; and the second best metric is $\hat\alpha$, which is an approximate log $\alpha$-Norm metric.
\michael{Are those numbers stale, I don't see them, and some things seem in the other order.}
\charles{See Figure 2}
\michael{We should probably point to the table if we cite quantitative results.}

@@

Table \ref{table:cv-models} summarizes results for all four metrics (Frobenius norm, Spectral norm, Weighted Alpha, and $\alpha$-Norm) applied to the VGG, ResNet, ResNet-1K, and DenseNet series.
\michael{XXX.  AGAIN, WHERE IS RMSE, IN THAT TABLE?}
\charles{The Table may be stale, see the figures to confirm}

@@

For the ResNet-1K models, $\alpha$ also increases in the last few layers, but as the models get deeper, there is a wide range over which $\alpha$ values tend to remain small.
\michael{Can we say something about exceptions which are larger than for VGG or DenseNet.}
\charles{You have the same plots I do..what do you want to say >}
This is seen for other models in the ResNet-1K series, but it is most pronounced for the larger ResNet-1K (152) model, where $\alpha$ remains relatively stable at $\alpha\sim 2.0$, from the earliest layers all the way until we reach close to the final layers.

### 2020-01-31 methods.tex
more edits

@@

\paragraph{XXX.}
XXX.  THIS VERIFICATION IS NOT ABOUT CONV LAYERS, IT IS ABOUT PL MORE GENERALLY, CORRECT?  WE SHOULD CLARIFY AND SQUISH.
To verify that our approach is meaningful, we need to confirm that the ESD is neither due to a random matrix, nor due to unsually large matrix elements, but, in fact, captures correlations learned from the data. 
We examine typical layer for the pretained AlexNet model (distributed with pyTorch). 
Figure~\ref{fig:alexnet1} displays the ESD for the first slice (or matrix $\mathbf{W}$) of the third Conv2D layer, extracted from a 4-index Tensor of shape $(384, 192, 3, 3)$.  The red line displays the best fit to a random matrix, using the Marchenko pastur theory~\cite{MM}.  We can see the random matrix model does not describe the ESD very well. For comparison, Figure \ref{fig:alexnet2} shows the ESD of the same matrix, randomly shuffled; here looks similar to the red line plot of the orginal ESD.  In fact, the empircal ESD is better modeled with a truncated power law distribtion.
\michael{We may want to give a one-sentence summary of this par and fig at the end of the previous par.}

@@

Although the ESD is \emph{Heavy Tailed}, this does not imply that the orginal matrix $\mathbf{W}$ is itself heavy tailed--only the correlation matrix $\mathbf{X}$ is. 
If $\mathbf{W}$ was, then it would contain 1 or more unusually large matrix elements, and they would dominate the ESD.  
Of course the randomized $\mathbf{W}$ would also be heavy tailed, but its ESD neither resembles the original nor is it heavy tailed. 
So we can rule out $\mathbf{W}$ being heavy tailed.
\michael{These comments seem out of place, since they hold more generally than for the Conv2D layers.}

>>>>

\charles{hard to confer on this.  I tried to state this as simply as possible.  We have never stated this before, and I think its going to be confusing.  We at least need to explain why we are looking at the average log norm. Otherwise we are forcing the reader to look back, and the paper is hard to read as a standalone entity. }

@@

\paragraph{XXX.}
XXX.  THIS VERIFICATION IS NOT ABOUT CONV LAYERS, IT IS ABOUT PL MORE GENERALLY, CORRECT?  WE SHOULD CLARIFY AND SQUISH.
To verify that our approach is meaningful, we need to confirm that the ESD is neither due to a random matrix, nor due to unsually large matrix elements, but, in fact, captures correlations learned from the data. 
We examine typical layer for the pretained AlexNet model (distributed with pyTorch). 
Figure~\ref{fig:alexnet1} displays the ESD for the first slice (or matrix $\mathbf{W}$) of the third Conv2D layer, extracted from a 4-index Tensor of shape $(384, 192, 3, 3)$.  The red line displays the best fit to a random matrix, using the Marchenko pastur theory~\cite{MM}.  We can see the random matrix model does not describe the ESD very well. For comparison, Figure \ref{fig:alexnet2} shows the ESD of the same matrix, randomly shuffled; here looks similar to the red line plot of the orginal ESD.  In fact, the empircal ESD is better modeled with a truncated power law distribtion.
\michael{We may want to give a one-sentence summary of this par and fig at the end of the previous par.}
\charles{Here, on the RMT MP stuff, I think it makes sense to point back}

@@

Although the ESD is \emph{Heavy Tailed}, this does not imply that the orginal matrix $\mathbf{W}$ is itself heavy tailed--only the correlation matrix $\mathbf{X}$ is. 
If $\mathbf{W}$ was, then it would contain 1 or more unusually large matrix elements, and they would dominate the ESD.  
Of course the randomized $\mathbf{W}$ would also be heavy tailed, but its ESD neither resembles the original nor is it heavy tailed. 
So we can rule out $\mathbf{W}$ being heavy tailed.
\michael{These comments seem out of place, since they hold more generally than for the Conv2D layers.}
\charles{Agreed. We could move this up.  We have never really talked about this, but it is essential to explain the difference between assuming W is heavy tailed , which confuses everyone}
